Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-14 snapshot_system/failover.tex
Added some to failover.text (added numbers for block<-VM links)

@@

\subsection{Empirical Validation}
To validate our theoritical model for the probability of data loss, we computed
the number of VMs using each block in a global index for the 350 VM traces.
As you can see in Fig.~\ref{??}, The average number of VMs sharing a block
%TODO: insert figure generated from data/links_no_cds.dat
increases linearly with the number of snapshots. For 350 snapshots there are an
average of 13.1 links to a given block in the global index.
%What else do we need from the simulation to validate the model?

\subsubsection{CDS and Fault Tolerance}
%all numbers in this paragraph need to be corrected after I re-run the tests
%using the actual cds generator code
As part of our emprirical validation of our model, we also computed the effects
of the CDS on fault tolerance. If we exclude the top 5\% most popular blocks
and set aside those in the CDS, the average number of links to a non-CDS block
%TODO: insert figure generated from data/links_cds.dat and data/links_wo_cds.dat
drops to 10.3 for 350 snapshots. This means that on average, \~3 fewer
snapshots will be affected by a lost data block in the general data store.
The average number of links to a CDS block however, for 350 snapshots, is
65.7. This suggests that a much higher replication factor is warranted for
the CDS, as on average, a CDS block appears in 19\% of all the snapshots.

>>>>

%the above model assumes uniform distribution of blocks and doesn't provide compelling numbers
%with 3 replicas, 100 machines, and only 3 failures the chance of a single 10GB VM surviving is 9.11*10^-8
%if we wanted to include it we probably want a model that includes containers, but that might be too complex
%to be useful.

@@

\subsection{Empirical Validation}
%To validate our theoritical model for the probability of data loss, we computed
%the number of snapshots using each block in a global index for the 350 snapshot
%traces. As you can see in Fig.~\ref{??}, The average number of VMs sharing a block
%%TODO: insert figure generated from data/links_no_cds.dat
%increases linearly with the number of snapshots. For 350 snapshots there are an
%average of 13.1 links to a given block in the global index.
To validate our theoretical model for the probability of data loss, we measured
the number of snapshots and VMs sharing data blocks for our 350 snapshot
dataset. As you can see in Fig.~\ref{??}, the average number of snapshots sharing
a block increases linearly with the number of snapshots. For 350 snapshots
there are an average of 13.1 incoming links to a given data block in the global
index. If we look at the number of VMs sharing a data block rather than
snapshots, in the full dataset on average 1.47 VMs point to a data block in the
index.
%What else do we need from the simulation to validate the model?

\subsubsection{CDS and Fault Tolerance}
%all numbers in this paragraph need to be corrected after I re-run the tests
%using the actual cds generator code
As part of our emprirical validation of our model, we also computed the effects
of the CDS on fault tolerance. If we exclude the top 5\% most popular blocks
and set aside those in the CDS, the average number of links to a non-CDS block
%TODO: insert figure generated from data/links_cds.dat and data/links_wo_cds.dat
drops to 10.3 for 350 snapshots. This means that on average, \~3 fewer
snapshots will be affected by a lost data block in the general data store.
The average number of links to a CDS block however, for 350 snapshots, is
65.7. This suggests that a much higher replication factor is warranted for
the CDS, as on average, a CDS block appears in \~20\% of all the snapshots.
These measured numbers are different from our theoritical model due to the fact
that duplicate data blocks are not uniformly distributed across all VMs.
With uniform distribution of duplicates (and a zipf distribution on the number
of duplicates), there should be on average 2.55 incoming VM links to each
block. Since we show the average number of links to be 1.47 in our actual
traces, the duplicates are
more tighly grouped than the uniform model would predict. This supports
the benefits of using a CDS plus more localized deduplication.
